---
  title: "R Notebook"
output:
  html_document:
  df_print: paged
---
  
  
  ```{r}
dat.merge <- read.csv("PopularMusicByAge.csv")

#creating a new column that is titled "Age Popular" on the data sheet becuase then we know the age of the participant WHEN the song was popular. 
dat.merge$AgePopular <- dat.merge$YearPopular-(2016-as.numeric(dat.merge$age_bucket))

#This is taking the age_bucket of the participant and seeing if it is less than 80 years, or if it is more than 25 years, and including only those rows. 
dat.merge <- dat.merge[(dat.merge$age_bucket<=80),]
dat.merge <- dat.merge[(dat.merge$age_bucket>=25),]
View(dat.merge)

summary(dat.merge)
newdata = dat.merge[,c(4,6,8)]
summary(newdata) #This gives the minimum/maximum/means for age bucket, ranking, and age popular.

#this gives a 3x3 sheet that looks at correlation between all the 3 variables. 
#plot(newdata, pch=3, col='blue', main= "Tryin' it out")

#Below gives that hella long list of songs and numbers after them.
#reg1 <-  lm(ranking~as.factor(track_name)+as.factor(age_bucket),data=dat.merge)
#summary(reg1) 

names(dat.merge) #gives the titles of the columns.

dat.merge.sub <- subset(dat.merge, ranking >=4001)
View(dat.merge.sub) #This gives a dataframe of all of the values that didn't have spotify data.

#Below gives hella long list of songs and numbers after them for datmerge for the songs in gender/age that don't have any info on Spotify.
#reg3 <- lm(ranking~as.factor(track_name)+as.factor(age_bucket),data=dat.merge.sub)
#summary(reg3) 

```

New trials with selected data with only 4 songs. 
```{r}
dat.merge2 <- read.csv("spotifySelectedData.csv")
dat.merge2$AgePopular <- dat.merge2$YearPopular-(2016-as.numeric(dat.merge2$age_bucket))

dat.merge2 <- dat.merge2[(dat.merge2$age_bucket<=80),]
dat.merge2 <- dat.merge2[(dat.merge2$age_bucket>=25),]
View(dat.merge2)

reg2 <- lm(ranking~as.factor(track_name)+as.factor(age_bucket),data=dat.merge2)
summary(reg2) #List of those four songs. 

newdata2 = dat.merge2[,c(4,6,8)]
summary(newdata2)
#Below is the weird 3x3 graphs of correlations between all 3 variables.
#pl2 <- plot(newdata2)  

```


```{r}
#Load ggplot!!
library(ggplot2)
#Load csv file I created ONLY with information from Janet Jackson's "That's The Way Love Goes"
dat.Janet <- read.csv("ThatsTheWayLoveGoes.csv")
View(dat.Janet)
#Create a new data that only has the Age Bucket, Ranking, and Gender in it. 
newdataJanet <- dat.Janet[,c(4,5,6)]
summary(newdataJanet)

gplotJanet <- ggplot(data=newdataJanet, aes(x=age_bucket, y=ranking)) +
  geom_point(aes(color=gender))+
  labs(title='Popularity by Age for Janet Jackson "That\'s the Way Love Goes"', x='Age Bucket (current, i.e., not adjusted to year)', y='Ranking (out of 4001)')

gplotJanet
gplotJanet + scale_y_reverse() #Reverses Y axis so higher the ranking the lower it is on the graph.

#Does a 3x3 weird graphing of correlations of the 3 variables. 
plot(newdataJanet)

```


```{r}
library(ggplot2)
dat.Savage <- read.csv("Truly Madly Deeply.csv")
View(dat.Savage)
newdataSavage <- dat.Savage[,c(4,5,6)]

summary(newdataSavage)
summary(newdataSavage$age_bucket)

gplotSavage <- ggplot(data=newdataSavage, aes(x=age_bucket, y=ranking, group=1)) +
  geom_point(aes(color=gender))+
  labs(title='Popularity by Age for Savage Garden "Truly Madly Deeply"', x='Age Bucket (current, i.e., not adjusted to year)', y='Ranking (out of 4001)')
gplotSavage
gplotSavage + scale_y_reverse() #Reverses Y axis so higher the ranking the lower it is on the graph.
```

The above two graphs look similar to the graphs under the Avg. Spotify Rank by Age in the NYT article. 

However, if you take another song that might not have that much of a correlation, like "96 Tears"...

```{r}
library(ggplot2)
dat.Tears <- read.csv("ninetySixTears.csv")
View(dat.Tears)
newdataTears <- dat.Tears[,c(4,5,6)]

summary(newdataTears)
summary(newdataTears$age_bucket)

gplotTears <- ggplot(data=newdataTears, aes(x=age_bucket, y=ranking, group=1)) +
  geom_point(aes(color=gender))+
  labs(title='Popularity by Age for ? and the Mysterians "96 Tears"', x='Age Bucket (current, i.e., not adjusted to year)', y='Ranking (out of 4001)')
gplotTears
gplotTears + scale_y_reverse() #Reverses Y axis so higher the ranking the lower it is on the graph.
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

